%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Deedy - One Page Two Column Resume
% LaTeX Template
% Version 1.2 (16/9/2014)
%
% Original author:
% Debarghya Das (http://debarghyadas.com)
%
% Original repository:
% https://github.com/deedydas/Deedy-Resume
%
% IMPORTANT: THIS TEMPLATE NEEDS TO BE COMPILED WITH XeLaTeX
%
% This template uses several fonts not included with Windows/Linux by
% default. If you get compilation errors saying a font is missing, find the line
% on which the font is used and either change it to a font included with your
% operating system or comment the line out to use the default font.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% 
% TODO:
% 1. Integrate biber/bibtex for article citation under publications.
% 2. Figure out a smoother way for the document to flow onto the next page.
% 3. Add styling information for a "Projects/Hacks" section.
% 4. Add location/address information
% 5. Merge OpenFont and MacFonts as a single sty with options.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% CHANGELOG:
% v1.1:
% 1. Fixed several compilation bugs with \renewcommand
% 2. Got Open-source fonts (Windows/Linux support)
% 3. Added Last Updated
% 4. Move Title styling into .sty
% 5. Commented .sty file.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Known Issues:
% 1. Overflows onto second page if any column's contents are more than the
% vertical limit
% 2. Hacky space on the first bullet point on the second column.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\documentclass[]{deedy-resume-openfont}
\usepackage{fancyhdr}
 
\pagestyle{fancy}
\fancyhf{}
 
\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     LAST UPDATED DATE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\lastupdated

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\namesection{Ahmed}{Mokhtar}{
\urlstyle{same}\href{mailto:ahmed.s.mokhtar@outlook.com}{ahmed.s.mokhtar@outlook.com} | \href{tel:+201116521603 }{+34634797948} | Madrid - Spain\\ \href{https://www.linkedin.com/in/ahmed-s-mokhtar/}{linkedin.com/in/ahmed-s-mokhtar} | \href{https://github.com/imokhtar}{github.com/imokhtar}\\

}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{1\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Experience}
\runsubsection{Amazon}
\location{| Madrid, Spain}
\descript{Software Engineer | Jul 2022 - Present}
\vspace{\topsep} 
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item Delivered a high level system design for a web-service that is part of an org-wide scope initiative. Through the design process I gathered and refined requirements with the initiative stakeholders. The design is utilizing AWS StepFunctions for batch processing orchestration.
\item Developed the service infrastructure, connectivity, CI/CD pipelines, and Auth while writing the infrastructure as code using AWS CDK.
\item Participated in developing a checkout frontend service using react, I designed the state management of the app using Redux.
\item Helped my team to fasten their local development by automating local environment setup and updating our services runbooks.
\end{tightemize}
\sectionsep
\runsubsection{Abjjad}
\location{| Amman, Jordan}
\descript{Senior iOS Developer | Nov 2020 - Present}
\descript{Part Time iOS Developer | Jun 2019 - Nov2020}
\vspace{\topsep} 
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item Led and shipped Abjjad iOS app - an app that was featured as "App of the Day" many times by Apple Editors. 
\item Developed an eReader framework to render Abjjad books. The framework produces a cutting-edge reading experience by utilizing TextKit, CoreText and UIKit frameworks.
\item Revamped the superscription feature of the app by improving UX, introducing promo-codes, and pausing and resuming functionalities using StoreKit's In-App-Purchase.
\item Enhanced app performance and memory footprint by utilizing Xcode profiling tools.
\item Made the code scalable, modular, and testable by applying Clean Architecture + MVVM.
\item Added support for iPadOS features such as multi-windows and multitasking.
\item Implemented CI/CD pipelines which builds, signs the code, run unit and functional tests, and publishes to App Store.
\item Fastened app start time and reduced app size by linking app dependencies statically.
\item Enabled marketing team to attribute and measure the conversion rates of running ad campaigns using different tools and techniques which are compatible with iOS 14.6 and later.
\end{tightemize}
\sectionsep

\runsubsection{BlaBla Connect}
\location{ | Cairo, Egypt}
\descript{iOS Developer | Dec 2018 – Oct 2020 }

\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item Delivered robust and maintainable code by following clean code best practices, applying the clean architecture to the project, and unit testing 90\% of the code.
\item Developed ID Verification feature by using Vision and CoreImage frameworks.
\item Ensured system integrity by writing fail-proof UI tests.
\end{tightemize}
\sectionsep

\runsubsection{Nagwa}
\location{ | Cairo, Egypt}
\descript{Mathematics Content Editor | Nov 2017 – Nov 2018 }
\vspace{\topsep}
\begin{tightemize}
\item Worked on classifying and indexing content based on its learning objectives.
\item helped manage curriculum plans to deliver high-quality math content.
\end{tightemize}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage} 
\hfill
\begin{minipage}[t]{1\textwidth} 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Education} 

\subsection{Asyut University}
\descript{Bachelor degree in Mathematics}
\location{2011 | Asyut, EG}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Skills}
\subsection{Programming Languages \& SDKs}
Swift (expert) \textbullet{} Objective-C (proficient) \textbullet{} Dart\ (proficient) \textbullet{} Python \textbullet{} JavaScript\ \textbullet{} Java\
\sectionsep
\subsection{Platforms}
iOS \textbullet{} Flutter \textbullet{} Backend\ \textbullet{} Frontend\ \textbullet{} AWS\
\sectionsep
\subsection{Frameworks \& Libraries}
SwiftUI \textbullet{} UIKit \textbullet{} React \textbullet{} SpringMVC \textbullet{} Guice \textbullet{}
Firebase \textbullet{} Realm \textbullet{} \\CoreText \textbullet{} TextKit \textbullet{} GCD \textbullet{} CoreImage \textbullet{} Vision \textbullet{} Travis \textbullet{} NodeJS\ (prior) \textbullet{} SQLite \textbullet{} SignalR \textbullet{} Stripe
\sectionsep
\subsection{AWS Services}
ECS/Fargate \textbullet{} ECS/EC2 \textbullet{} ALB and NLB \textbullet{} ECR \textbullet{} Route53 \textbullet{} IAM \textbullet{} S3 \textbullet{} DynamoDB \textbullet{} CloudFormation
\sectionsep
\subsection{Software Skills}
System Design \textbullet{} Design Patterns \textbullet{} OOP \textbullet{} OOD \textbullet{}\\ Reactive Programming \textbullet{} \\ Functional Programming \textbullet{} Unit Testing \textbullet{} UI Testing
\sectionsep
\subsection{Other Skills}
Abstract thinking \textbullet{} Agile (Scrum)
\sectionsep


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Own Projects
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Own Projects}
\subsection{Egypt Trains Android}
An app to show the timetables of ENR.
I leveraged knowledge in Flutter, BLoC, Dart, RxDart, Clean Architecture.
\sectionsep
\subsection{Egypt Trains iOS}
Since it was launched in 2019, it is among the top 5 Travel apps in the app store with a 4.6 rate from over 3k users and 100\% crash-free users
\sectionsep
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Languages
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Languages}
Arabic (native) \textbullet{} English (very good)
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Hobbies
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Hobbies}
Walking \textbullet{} Running \textbullet{} Gaming
\end{minipage} 
\end{document}  \documentclass[]{article}
